The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-29 manuscript/manuscript.Rnw
fix wrong oxford comma

Even though the placenta's primary function is conserved among
mammals, it varies widely in terms of the shape of attachment, degree
of intimacy between fetal tissues and maternal tissues and degree of
interdigitation of maternal and fetal tissues in different species of
mammals
\cite{Mossman.1987:vertebratefetalmembranes} %,Moffett.ea2006:Immunologyofplacentationin}
(Supplemental \cref{tab:placental_classification}). Mammals also
differ drastically in the number and size of their offspring, as well
as the length of gestation; these traits are often associated with
specific aspects of placental morphology
\cite{Capellini.ea2011:Placentationandmaternalinvestment}
(Supplemental \cref{tab:gestational_periods}). Although the morphology
of the mammalian placenta has been well characterized in a number of
species \cite{Mossman.1987:vertebratefetalmembranes}, the diversity of
the molecular environment is only beginning to be understood from a
genetic perspective \cite{Carter2012:Evolutionofplacentalfunction}.

>>>>

Even though the placenta's primary function is conserved among
mammals, it varies widely in terms of the shape of attachment, degree
of intimacy between fetal tissues and maternal tissues, and degree of
interdigitation of maternal and fetal tissues in different species of
mammals
\cite{Mossman.1987:vertebratefetalmembranes} %,Moffett.ea2006:Immunologyofplacentationin}
(Supplemental \cref{tab:placental_classification}). Mammals also
differ drastically in the number and size of their offspring, as well
as the length of gestation; these traits are often associated with
specific aspects of placental morphology
\cite{Capellini.ea2011:Placentationandmaternalinvestment}
(Supplemental \cref{tab:gestational_periods}). Although the morphology
of the mammalian placenta has been well characterized in a number of
species \cite{Mossman.1987:vertebratefetalmembranes}, the diversity of
the molecular environment is only beginning to be understood from a
genetic perspective \cite{Carter2012:Evolutionofplacentalfunction}.
